---
title: "Milestone 6"
author: "Alexander Klueber"
date: "4/03/2020"
output: bookdown::pdf_document2
bibliography: Bibliography.bib
citations: natbib
link-citations: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::write_bib(c("blei", "cai", "horsley", "jiang", "un", "seifert", "pan"), "Bibliography.bib", width = 60)
library(tidyverse)
library(stargazer)
library(tinytex)
library(gtable)
library(gt)
```

# Results

## Section 3.1: Website Content

### Figure 1: County Government Website Availability by Province

```{r section_3_1_website_content_figure_1}

# loading in the countywebsites data set (which lists the websites for all chinese counties that had them in place (2,867 counties))

countyweb <- read.csv("raw-data/countywebsites.csv") 


# Returning the dimensions in the data set (2,867 lines (counties) and 5 variables)

  #dim(countyweb) #2,867 counties


# Filtering out the counties for which there is no website and assigning them to a data frame called countyweb_na

countyweb_na <- countyweb[countyweb$Website == "",]


# Counting the number of counties in that data frame

  #dim(countyweb_na) # 80 counties without websites


# Counting the number of counties that have websites by subtracting the first dimension of the countyweb_na (that contains the counties that do not have a website) data frame from the first dimension of all counties included in the countyweb data frame

  #dim(countyweb)[1] - dim(countyweb_na)[1]  # 2,787 counties with websites

# Counting the number of provinces represented through the 80 counties by counting the length of a vector that includes only the unique provinces in the countyweb_na data frame 

  #length(unique(countyweb_na$Province)) # 80 counties in 20 provinces


# Fig 1: Proportion of counties without websites by province
# Creating the prportion of counties without website in all provinces by dividing the tabled number of rows in a province from the countyweb_na data frame by the tabled number of rows in a province from the data frame that includes all counties

table(countyweb_na$Province) / table(countyweb$Province)
```

```{r section_3_1_website_content_sample}
# 100 randomly sampled counties
# Loading in a random sample of 100 county websites, that are separated by a tab

county100 <- read.csv("raw-data/countywebsites_sampled100.csv", sep="\t") 


# Listing the column names of this sample

  # colnames(county100)


# Counting the number of provinces represented through the 100 random counties by counting the length of a vector that includes only the unique provinces in the countyweb_na data frame 

  # length(unique(county100$province_en))  # 100 counties in 29 provinces


# Building a count table of the two different county types (county-level cities or counties and districts)

  # table(county100$countytype) # 61 are county-level cities or counties, 39 are districts


# Building a count table of the three different macro-regions (Central, East, West)

  # table(county100$macroregion) # 34 in West China, 31 in Central, 35 in East


# For the random sample of 100, summing up the total number of links found from root url of countyurl across all counties, removing missing values with na.rm = TRUE 

  # sum(county100$linksall, na.rm=T) #2,015,061 links among all 100


# For the random sample of 100, summing up the total number of links found from root url of countyurl that were internal to website across all counties, removing missing values with na.rm = TRUE

  # sum(county100$linksint, na.rm=T) # 1,547,239 internal links


# Getting a summary of descriptive statistics for the number of links internal to the website in the random sample of 100 counties, given that they had more than 0 internal links, indicating a range from 49 to 162403 internal links

  # summary(county100$linksint[county100$linksint >0]) # range from 49 to 162,400, for website where links could be obtained


# Number of websites that had more than 100 scraped links that contained chinese text in a count table 

  # table(county100$links_chtxt > 100) # 71 counties with >100 Chinese web pages

```

## Section 4.1: Topics

### Table 1: LDA topics and OGI Requirements

```{r section_4_1_topics_table_1}
# Loading in output of LDA topic model, including topic number (topic), hand label (label), corresponding ogi category (obi), and the top 50 words in Chinese with the word frequency (word1, word2, etc.), separating the columns by tabs

topics <- read.csv("raw-data/topics.csv",stringsAsFactors=F, sep="\t")


# listing the column headers of the topics data frame

  # colnames(topics)


# Counting the number of dimensions in the data set (50 different topics)

  # dim(topics)  # 50 topics


# Create count table of number of topics that were unable to label (11) vs. 39 that were able to lable

  # table(topics$label == "unable to label")  # could lable 39 topics

# Table 1
# Looking at the topics that are included under the respective ogi clusters

print("OGI: administrative rules and regulations")
topics$label[topics$ogi=="administrative rules and regulations"]

print("OGI: economic development plans")
topics$label[topics$ogi=="economic development plans"]

print("OGI: statistical information")
topics$label[topics$ogi=="statistical information"]

print("OGI: budgets and financial accounts")
topics$label[topics$ogi=="budgets and financial accounts"]

print("OGI: procurement standards")
topics$label[topics$ogi=="procurement standards"]

print("OGI: administrative licensing")
topics$label[topics$ogi=="administrative licensing"]

print("OGI: major construction projects")
topics$label[topics$ogi=="major construction projects"]

print("OGI: land acquisition and housing demolition")
topics$label[topics$ogi=="land acquisition and housing demolition"]

print("OGI: poverty alleviation, education, health care, social security, employment")
topics$label[topics$ogi=="poverty alleviation, education, health care, social security, employment"]

print("OGI: emergency management plans")
topics$label[topics$ogi=="emergency management plans"]

print("OGI: environment, product quality and supervision")
topics$label[topics$ogi=="environment, product quality and supervision"]

print("OGI: other")
topics$label[topics$ogi=="other"]
```

## Section 5.1: Measuring Tenure

### Table 2: Distribution of Year in office

```{r section_5_1_measuring_tenure_table_2}
county100 <- read.csv("raw-data/countywebsites_sampled100.csv", sep="\t") 

# Table 2: Distribution of Year in Office
# Creating a count table based of the number of counties in which the mayor has been in office for a certain number of years ( 1- 6 years)

distr <- county100 %>%
  group_by(mayor_tenure2) %>%
  summarise(`Number of Counties` = n()) %>%
  drop_na()

prop <- county100 %>%
  group_by(mayor_tenure2, mayor_status) %>%
  summarise(`Number of Counties` = n()) %>%
  drop_na()%>%
  spread(key = mayor_status, value = `Number of Counties`) %>%
  mutate(`in office` = ifelse(is.na(`in office`), 0 , `in office`),
         promotion = ifelse(is.na(promotion), 0 , promotion),
         retired_demoted = ifelse(is.na(retired_demoted), 0 , retired_demoted),
          Total = `in office`+ promotion + retired_demoted,
         `Stayed in Same Position` = round(`in office`/Total,2),
          Promoted = round(promotion/Total,2),
          `Retired or Demoted` = round(retired_demoted/Total,2)) %>%
  select(`Stayed in Same Position`, Promoted, `Retired or Demoted`, mayor_tenure2)
  
table <- bind_cols(prop, distr) %>%
        select (-mayor_tenure21)

gt_table <- 
  table %>%
  gt(
    rowname_col = "mayor_tenure2",
    groupname_col = "group"
  )


gt_table %>% 
  tab_stubhead(label = "Years in Office") %>%
  tab_header(
    title = "Table 2: Distribution of Year in office",
    subtitle = "Based on sample of 100 counties") %>%
  fmt_percent(
    columns = vars("Stayed in Same Position", "Promoted", "Retired or Demoted"),
    decimals = 0) %>%
  cols_align("center")

```

## Section 5.2: Descriptive Results

### Figure 2: Proportion of web pages with content focused on competence by year in office...

```{r section_5_2_descriptive_results_figure_2}
# Replicating Figure 2 on page 15 of the paper 

# Loading in statistical analysis estimating the competence/benevolence level and lower and upper boundaries based on how many years an official has been in office 
# readme_out_yroff.csv: estimated proportion of posts for competence and benevolence by year in office, where group refers to the year, with 95% confidence intervals in lwr and upr. Generated using Hopkins and King (2010) ReadMe software

yroff <- read.csv("raw-data/readme_out_yroff.csv", header=TRUE)


# Loading in statistical analysis estimating the competence/benevolence level and lower and upper boundaries based on the proximity to tenure

# readme_out_tenure.csv: estimated proportion of posts for competence and benevolence by proximity to leaving office, where group = 1 refers beginning of tenure, group = 2 to middle of tenure, and group = 3 to end of tenure; 95% confidence intervals in lwr and upr. Generated using Hopkins and King (2010) ReadMe software

tenure <- read.csv("raw-data/readme_out_tenure.csv", header=TRUE)


# Defining y axis

yaxtloc <- c(0,.1,.2,.3,.4,.5)


# Labeling y axis

laxtlab <- c("0%", "10%","20%","30%","40%","50%")


# Defining x axis

xaxtloc <- c(0,.2,.4,.6,.8,1)


# Labeling x axis

lxaxtlab <- c("Beginning", "Middle","End")


# Fig 3: Proportion of web pages with content focused on competence   

# Setting the layout parameters in terms of how much they ought to be magnified in comparison to the defaul for the graph as 1,2 

par(mfrow=c(1,2)) 

# Creating a plot containing all x values from 1 to 5 years of office, and the respective estimate values as the dots in the graph, setting the y axis to run from 0 to 50%, setting the size of the dots to 16 and defining the x and y labels, the width a and the size of the ticks on c and y axis and the labels

plot(1:5, yroff[1:5,]$estimate,ylim=c(0,0.5), pch=16,xlab="Year in Office",ylab="% Web Pages for Competence",cex=1.5, cex.axis=1.5, cex.lab=1.5,yaxt="n")
axis(2, at= yaxtloc,labels= laxtlab, cex.axis=1.5)

# Using a loop to add the upper and lower boundaries of width 2 for each of the years in office (1-5)

for(i in 1:5){
	segments(i,yroff[i,]$lwr,i,yroff[i,]$upr, lwd=2)
}


# Creating a plot containing all x values from 1 to 3 proximity to tenure, and the respective estimate values as the dots in the graph, setting the y axis to run from 0 to 50%, setting the size of the dots to 16 and defining the x and y labels, the width a and the size of the ticks on c and y axis and the labels

plot(1:3, tenure[1:3,]$estimate,ylim=c(0,0.5), pch=16,xlab="Proximity to Leaving Office",ylab="% Web Pages for Competence",cex=1.5, cex.axis=1.5, cex.lab=1.5,xaxt="n",xlim=c(0.8,3.2),yaxt="n")
axis(2, at= yaxtloc,labels= laxtlab, cex.axis=1.5)
axis(1,at=c(1,2,3),labels= lxaxtlab,cex.axis=1.5)


# Using a loop to add the upper and lower boundaries of width 2 for each of the proximities to tenure (1-3)

for(i in 1:3){
	segments(i,tenure[i,]$lwr,i,tenure[i,]$upr, lwd=2)
}

```

### Figure 3: Proportion of web pages with content focused on belevolence by year in office...

```{r section_5_2_descriptive_results_figure_3}
# Fig 4: Proportion of web pages with content focused on benevolence

# Setting the layout parameters in terms of how much they ought to be magnified in comparison to the defaul for the graph as 1,2 

par(mfrow=c(1,2)) 


# Creating a plot containing all x values from 1 to 5 years of office, and the respective estimate values as the dots in the graph, setting the y axis to run from 0 to 50%, setting the size of the dots to 16 and defining the x and y labels, the width a and the size of the ticks on c and y axis and the labels

plot(1:5, yroff[6:10,]$estimate,ylim=c(0,0.5), pch=16,xlab="Year in Office",ylab="% Web Pages for Benevolence",cex=1.5, cex.axis=1.5, cex.lab=1.5,yaxt="n")
axis(2, at= xaxtloc,labels= laxtlab, cex.axis=1.5)


# Using a loop to add the upper and lower boundaries of width 2 for each of the years in office (1-5)

for(i in 1:5){
	segments(i,yroff[i+5,]$lwr,i,yroff[i+5,]$upr, lwd=2)
}


# Creating a plot containing all x values from 1 to 3 proximity to tenure, and the respective estimate values as the dots in the graph, setting the y axis to run from 0 to 50%, setting the size of the dots to 16 and defining the x and y labels, the width a and the size of the ticks on c and y axis and the labels

plot(1:3, tenure[4:6,]$estimate,ylim=c(0,0.5), pch=16,xlab="Proximity to Leaving Office",ylab="% Web Pages for Benevolence",cex=1.5, cex.axis=1.5, cex.lab=1.5,xaxt="n",xlim=c(0.8,3.2),yaxt="n")
axis(2, at= yaxtloc,labels= laxtlab, cex.axis=1.5)
axis(1,at=c(1,2,3),labels= lxaxtlab,cex.axis=1.5)


# Using a loop to add the upper and lower boundaries of width 2 for each of the proximities to tenure (1-3)

for(i in 1:3){
	segments(i,tenure[i+3,]$lwr,i,tenure[i+3,]$upr, lwd=2)
}
```

## Section 5.3: Predictive Inference

### Table 3: Regression Results: Competence

```{r section_5_3_predictive_inference_table_3_data}
# load in 71 counties with over 100 Chinese language web pages, with svm predictions 

bycounty2 <- read.csv("raw-data/predict.csv")


# Create a statistical summary of the linear regression model that regresses a mayor first year or last year binary indicator on  he number of competence metnions on the websites by county

# Table 3 (1)
linear_1 <- lm(comp ~ mayor_first + mayor_last, data=bycounty2)  # ALMOST: mayo first yr more compolence

  # Adds county 2009 gdp per capita and proportion of county population over the age of 15 who are illiterate and number of county resident employed in information production, wholesale and retail from the 2010 census and total links found from root url of countyurl and 2009 provincial level expenditure on culture and media multiplied by the ratio of county GDP to province GDP
  
# Table 3 (2)
linear_2 <- lm(comp ~ mayor_first +mayor_last +X2009_gdppc_cny+X2010_illiterateprop+itemploy + linksall+ county_mediaexp, data=bycounty2)


# Adds whether county party secretary is in first year of office; takes on value of 1 if sec_2011 = 1, 0 otherwise and whether county party secretary is in last year of office; takes on value of 1 if sec_2011 = 1, 0 otherwise
# Table 3 (3)

linear_3 <- lm(comp ~ mayor_first + mayor_last + X2009_gdppc_cny + X2010_illiterateprop+itemploy + linksall+ county_mediaexp + sec_first + sec_last, data=bycounty2)


# Adds whether whether prefecture party secretary is in first or last year of office; takes on value of 1 if pref_ps_2011 = 1, 0 otherwise and evel of education of the prefecture party secretary at the end of formal schooling (not education while a government official); 6 = Doctoral degree; 5 = Master's degree; 4 = Bachelor's degree; 3 = degree from junior college; 2 = high school, 1 = lower than junior college and gdp per capita of the prefecture in 2010 

# Table 3 (4)
linear_4 <- lm(comp ~ mayor_first + mayor_last + X2009_gdppc_cny + X2010_illiterateprop+itemploy + linksall+ county_mediaexp + sec_first + sec_last + pref_ps_first + pref_ps_last + pref_ps_edulevel + pref_2010_gdppc, data=bycounty2) 


# Adds mayor age, mayor gender and mayor education level

# Table 3 (5)
linear_5 <- lm(comp ~ mayor_first + mayor_last + X2009_gdppc_cny + X2010_illiterateprop+itemploy + linksall+ county_mediaexp + sec_first + sec_last + pref_ps_first + pref_ps_last + pref_ps_edulevel + pref_2010_gdppc + mayor_age + mayor_gender + mayor_edulevel, data=bycounty2)


# Adds mayor promotion

# Table 3 (6)
linear_6 <- lm(comp ~ mayor_first + mayor_last + X2009_gdppc_cny + X2010_illiterateprop+itemploy + linksall+ county_mediaexp + sec_first + sec_last + pref_ps_first + pref_ps_last + pref_ps_edulevel + pref_2010_gdppc + mayor_age + mayor_gender + mayor_edulevel+ mayor_promote, data=bycounty2)

```

```{r section_5_3_predictive_inference_table_3_stargazer,  results="asis", echo=FALSE}

stargazer(linear_1, linear_2, linear_3, linear_4, linear_5, linear_6, # The various models included in the table
          title="Table 3: Regression Results: Competence", # The title of the table
          dep.var.caption = c("Dependent variable: Competence"), # The Caption of the table
          dep.var.labels.include=FALSE, # Don't include dependent variable labels
          no.space=TRUE, 
          keep.stat="n", # Include number of observation
          keep = c("mayor_first", "mayor_last", "Constant"),# exclude all variables, except the specified ones
          table.layout ="=l-c-t-a-s=n", # Detailing table layout according to replication paper (first dependent variable caption, then column headers, then coefficient table, then added lines, then summary statistics, then notes)
          add.lines=list(c("Resource controls",
                           rep("No", 1),rep("Yes",5)),
                        c("Peer controls",
                           rep("No", 2),rep("Yes",4)),
                        c("Prefecture controls",
                           rep("No", 3),rep("Yes",3)),
                        c("Ability controls",
                           rep("No", 4),rep("Yes",2)),
                        c("Career paths controls",
                           rep("No", 5),rep("Yes",1))), # Add lines to describe in categories the series of variables included
                        covariate.labels = c("Beginning Tenure", "End Tenure"),
                        float = FALSE) # Rename coefficient labels


# Note: Default type is Latex
```

### Table 4: Regression Results: Benevolence

```{r section_5_3_predictive_inference_table_4_data}
# Table 4 (1)
linear.1 <- lm(benev ~ mayor_first + mayor_last, data=bycounty2)

# Table 4 (2)
linear.2 <- lm(benev ~ mayor_first +mayor_last +X2009_gdppc_cny+X2010_illiterateprop+itemploy + linksall+ county_mediaexp , data=bycounty2)

# Table 4 (3)
linear.3 <- lm(benev ~ mayor_first + mayor_last + X2009_gdppc_cny + X2010_illiterateprop+itemploy + linksall+ county_mediaexp  + sec_first + sec_last, data=bycounty2)

# Table 4 (4)
linear.4 <- lm(benev ~ mayor_first + mayor_last + X2009_gdppc_cny + X2010_illiterateprop+itemploy + linksall+ county_mediaexp  + sec_first + sec_last + pref_ps_first + pref_ps_last + pref_ps_edulevel + pref_2010_gdppc, data=bycounty2)

# Table 4 (5)
linear.5 <- lm(benev ~ mayor_first + mayor_last + X2009_gdppc_cny + X2010_illiterateprop+itemploy + linksall+ county_mediaexp + sec_first + sec_last + pref_ps_first + pref_ps_last + pref_ps_edulevel + pref_2010_gdppc + mayor_age + mayor_gender + mayor_edulevel, data=bycounty2)

# Table 4 (6)
linear.6 <- lm(benev ~ mayor_first + mayor_last + X2009_gdppc_cny + X2010_illiterateprop+itemploy + linksall+ county_mediaexp + sec_first + sec_last + pref_ps_first + pref_ps_last + pref_ps_edulevel + pref_2010_gdppc + mayor_age + mayor_gender + mayor_edulevel+ mayor_promote, data=bycounty2)

```


```{r section_5_3_predictive_inference_table_4_stargazer,  results="asis", echo=FALSE}

stargazer(linear.1, linear.2, linear.3, linear.4, linear.5, linear.6, # The various models included in the table
          title="Table 3: Regression Results: Benevolence", # The title of the table
          dep.var.caption = c("Dependent variable: Benevolence"), # The Caption of the table
          dep.var.labels.include=FALSE, # Don't include dependent variable labels
          no.space=TRUE, 
          keep.stat="n", # Include number of observation
          keep = c("mayor_first", "mayor_last", "Constant"),# exclude all variables, except the specified ones
          table.layout ="=l-c-t-a-s=n", # Detailing table layout according to replication paper (first dependent variable caption, then column headers, then coefficient table, then added lines, then summary statistics, then notes)
          add.lines=list(c("Resource controls",
                           rep("No", 1),rep("Yes",5)),
                        c("Peer controls",
                           rep("No", 2),rep("Yes",4)),
                        c("Prefecture controls",
                           rep("No", 3),rep("Yes",3)),
                        c("Ability controls",
                           rep("No", 4),rep("Yes",2)),
                        c("Career paths controls",
                           rep("No", 5),rep("Yes",1))), # Add lines to describe in categories the series of variables included
          covariate.labels = c("Beginning Tenure", "End Tenure"),
          float = FALSE) # Rename labels of coefficients

# Note: Default type is Latex
```


# Not replicated

## Section 3.1: Website Content

### Figure 1

I have not replicated the figure 1, a map of the various provinces in China and the availability of county government websites in them. This is because this was a manual step in the construction of the paper. I have replicated the data that was used as a basis for that map.

## Section 4.1: Topics

### Table 1

I have generated the underlying data for the table. I have not transferred it into the same table form as outlined in the paper.

## Section 5.3: Predictive Inference

### Table 3: Regression Results: Competence

Replicated the table, except positioning the constant at the bottom of the table

### Table 4: Regression Results: Benevolence

Same as above

# Proposed extension

I am interested to look into the variance of these results between different provinces in China. I think it would be fascinating to understand whether the observed effect holds true throughout the country. The author of the paper wants to contribute to the discussion around the internet in authoritarian regimes. At the same time, I am not convinced that she actually does. This is because the suggested signalling may very well be caused by cultural differences, arther than the nature of the regime. Understanding whether regional variances in China exist would help us evaluate the strength of this competing hypothesis to explain the observations. 

In addition, i want to see whether this observations varies by gender of the official, education level or gdp of the county If there is any significant deviance across these coefficients, it would give potency to other competing hypothesis than that of an authoritarian regime. It might suggest that gender, education level or the wealth of a a county are more decisive in determining the self-portrayal of officials than their tenure. The reason this and the above is relevant, is because the author suggests that it is primarily an internal signalling function that these websites and the emphasis on certain factors serve. The link between tenure and the promotional expectations relate to that. proving that it is in fact not tenure, but one of the other factors that have nothing to do with the career path of the individuals within the party, would weaken that connection.

This endevour is constrained by the data available in the dataverse associated to the replication paper. Only the pre-selected sample of 100 contains all variables relevant for the analysis on a county level. Therefore a sub-division of that data by provinces will leave us with very small sample sizes. Similarly, the sample only contains 4 female mayors, 1 person with education level 6, 4 people with education level 5, 3 people with education levle 2 and 2 people with education level 0. 

The other part of my extension will be around challenging the data selection process conducted in the paper. It seems very surprising that the author has sub-selected 100 of the 2,787 counties with website, and we immediately dismiss another ~30 in our regressions because of data inavailability and subsequentyl another ~20 as our regressions get more ambitious. The absence of any website from Tibet is furthermore conspicuous. The way by which I seek to challenge this is to compare the observed characteristics of the sample, to what we would expect in repeated sampling from the underlying population in terms of frequency of different provinces and in terms of data availability. This will allow us do deduct how representative the sample actually is for the underlying population. Significant deviances will have us question the validity of the sampling procedure and as a result the conclusions drawn by the author based on that sample.   